Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
using bibtex.

\item @kazu: Can you add a reference to:
\url{http://www.haskell.org/cabal/users-guide/developing-packages.html#test-suites}

@@

\noindent Cabals test feature can be used to automatically run tests.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and Hspec in a single cabal file.

@@

% We recommend abbrvnat bibliography style.

\bibliographystyle{abbrvnat}

% The bibliography should be embedded for final submission.

\begin{thebibliography}{}
\softraggedright

\bibitem[Wadler 1989]{free}
Wadler P.,
``Theorems for free!'',
In proceeding of 4th International Conference on Functional Programming and Computer Architecture, 1989.

\bibitem[Claessen et al. 2000]{quickcheck}
Claessen K. and Hughes J.,
``QuickCheck: a lightweight tool for random testing of Haskell programs'',
ICFP '00 Proceedings of the fifth ACM SIGPLAN international conference on Functional programming,
pp 268 -- 279,
2000

\bibitem[Marlow et al. 2010]{haddock}
Marlow S. and Waern D.,
``Haddock User Guide'',
URL http://www.haskell.org/haddock/doc/html/,
2010

\bibitem[Python 2012]{doctest}
Python Software Foundation,
``Python documentation'',
URL http://docs.python.org/library/doctest.html,
2012

\bibitem[Chelimsky et al. 2010]{rspec}
Chelimsky D.,
Astels D., Dennis Z., Hellesoy A., Helmkamp B., and North D.,
``The RSpec Book: Behaviour-Driven
Development with RSpec, Cucumber, and Friends'',
2010
%% Hellesoy -- o/

\end{thebibliography}

>>>>

@@

\noindent Cabals test feature can be used to automatically run tests~\cite{cabal}.  A cabal
file can contain multiple test suites, so it is possible to define test suites
for Doctest and Hspec in a single cabal file.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrvnat}
\bibliography{refs}
